A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

A lot of work has been carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, King1996, Indelman_1993, Vereecken_2007, Wen_1996, Yeo2001}. \citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for an oil reservoir with varying permeabilities. The general conclusion reached from this study was that the equivalent permeability lies between the harmonic and the arithmetic average.

>>>>

Several studies were carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, King1996, Indelman_1993, Vereecken_2007, Wen_1996, Yeo2001}. \citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for oil reservoirs with varying permeabilities. The general conclusion reached from this study was that the equivalent permeability lies between the harmonic and the arithmetic average.
